R Notebook

### 2023-03-23 Analysis tests.Rmd
Created a notebook to run the MGWR and write it in a geopackage in the same format as the R output

```{r}
df_new <- df %>% 
  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4),
         addressline_zip = paste(zip, letters),
         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
  select(-optional1, -optional2, -optional3, -optional4) %>% 
  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")

```
```{r}

@@

```{r}
multiGWR <- gwr.multiscale(price~room +living_area + house_age, 
                        data = greendata_sp,
                        adaptive = T, 
                        max.iterations = 10, #usually large number to make sure each variable converage to best bandwidth
                        criterion="CVR", #criterion for determining the convergence of the back-fitting procedure
                        kernel = "gaussian", #kernel can also be gaussian, exponential
                        bws0=c(10,10,10), #starting number of neighbors  
                        verbose = F, predictor.centered=rep(T, 6),
                        parallel.method = "omp") 
```

@@

```{r}
mgwr_sf = st_as_sf(multiGWR$SDF)
st_write(mgwr_sf, "data/test/test_sample(100p)_predictions.gpkg")
```

```{r}
mgwrM1 <- mapview::mapview(mgwr_sf, zcol = "room", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
mgwrM2 <- mapview::mapview(mgwr_sf, zcol = "living_area", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
mgwrM3 <- mapview::mapview(mgwr_sf, zcol = "house_age", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
```

```{r}
sync(mgwrM1, mgwrM2, mgwrM3)
```

>>>>

```{r}
df_new <- df %>% 
  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4),
         addressline_zip = paste(zip, letters),
         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
  select(-optional1, -optional2, -optional3, -optional4) %>% 
  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
#write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")
#df_new %>% 
#  select(longitude, latitude, price, room, living_area, house_age) %>% 
#  write.csv("data/test/mgwr.csv")
```
```{r}

@@

```{r}
EUDM <- gw.dist(coordinates(greendata_sp))

multiGWR_test <- gwr.multiscale(price~room +living_area + house_age, 
                        data = greendata_sp,
                        max.iterations = 1,
                        adaptive = T,  #usually large number to make sure each variable converage to best bandwidth
                        criterion="CVR", #criterion for determining the convergence of the back-fitting procedure
                        kernel = "gaussian", #kernel can also be gaussian, exponential
                        bws0 =c(93,48,46,70),
                        bw.seled = c(T,T,T,T), dMats=list(EUDM,EUDM,EUDM)) 
```
```{r}
gwr.predict(multiGWR_test, data = )
```

@@

```{r}
#mgwr_sf = st_as_sf(multiGWR$SDF)
#mgwr_sf <- st_read("test_sample(100p)_predictions")
mgwr_sf <- st_read("data/test/test_mgwr.gpkg")

```{r}
mgwrM1 <- mapview::mapview(mgwr_sf, zcol = "room", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
mgwrM2 <- mapview::mapview(mgwr_sf, zcol = "living_area", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
mgwrM3 <- mapview::mapview(mgwr_sf, zcol = "house_age", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
mgwrM4 <- mapview::mapview(mgwr_sf, zcol = "residual", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
```

```{r}
sync(mgwrM1, mgwrM2, mgwrM3,mgwrM4)
```
